---
title: "ICDM 2015"
author: "Thuy Quach"
date: "July 16, 2015"
output: html_document
---

This documents explores the data of the Kaggle competition: Drawnbrigde Cross-Device Connections ICDM 2015

The Website of the Kaggle competition is https://www.kaggle.com/c/icdm-2015-drawbridge-cross-device-connections

```{r Set dictionary}
getwd()
setwd("/Users/Thuy/Documents/ICDM 2015")
list.files()
```

Install readr and xtable

```{r, readr}
install.packages('readr', repos="http://cran.rstudio.com/")
install.packages('xtable', repos="http://cran.rstudio.com/")
library(readr)
library(xtable)

```

Install dplyr
```{r}
install.packages('dplyr',repos="http://cran.rstudio.com/")
install.packages('ggplot2', repos="http://cran.rstudio.com/")
install.packages('data.table', repos="http://cran.rstudio.com/")
library(dplyr)
library(ggplot2)
library(data.table)
  
```

# Load the data

```{r}
train <- read.csv("../ICDM 2015/dev_train_basic.csv")
test <- read.csv("../ICDM 2015/dev_test_basic.csv")
cookie <- read.csv("../ICDM 2015/cookie_all_basic.csv")
```

## Fix bad csv
Three files (id_all_ip.csv, id_all_property.csv, and property_category.csv) don’t have to a valid CSV file format. We will fix it by writting new function.

```{r Read bad csv}
read_bad_csv <- function(file_name, bad_col=3, n_max=-1) {
  f_in <- file(file_name)
  lines <- readLines(f_in, n=n_max)
  close(f_in)
  temp_csv_1 <- tempfile()
  f_out_1 <- file(temp_csv_1, "w")
  writeLines(gsub("\\{|\\}", '"', lines), f_out_1)
  close(f_out_1)
  data <- read_csv(temp_csv_1, col_names=FALSE)
  temp_csv_2 <- tempfile()
  f_out_2 <- file(temp_csv_2, "w")
  for (i in 1:nrow(data)) {
    bad_lines <- strsplit(substr(data[i,bad_col], 2, nchar(data[i,bad_col])-1), "\\),\\(")[[1]]
    if (bad_col==1) {
      lines <- paste(bad_lines,
                     paste0(as.character(data[i,2:ncol(data)]), collapse=","),
                     sep=",")
    } else if (bad_col<ncol(data)) {
      lines <- paste(paste0(as.character(data[i,1:bad_col-1]), collapse=","),
                     bad_lines,
                     paste0(as.character(data[i,bad_col+1:ncol(data)]), collapse=","),
                     sep=",")
    } else {
      lines <- paste(paste0(as.character(data[i,1:ncol(data)-1]), collapse=","),
                     bad_lines,
                     sep=",")
    }
  writeLines(lines, f_out_2)
  }
  close(f_out_2)
  return(read_csv(temp_csv_2))
}
```

## Load data with bad csv

```{r}
ip <- read_bad_csv("../ICDM 2015/id_all_ip.csv", bad_col=3, n_max=100)
property <- read_bad_csv("../ICDM 2015/id_all_property.csv", bad_col = 3, n_max = 100)
property_category <- read_bad_csv("../ICDM 2015/property_category.csv", bad_col=3, n_max=100)
```

# Summary of data set

## Device train set

```{r Train}
dim(train)
names(train)
str(train)
summary(train)
head(train)
```
### Observation
There are 1427770 devices in training set.


### Visualization

```{r Train Device-type}
p1 <- train %>%
  group_by(device_type) %>%
  summarize(count=length(device_type)) %>%
  ggplot(aes(x =device_type, y = count)) +
    geom_bar(fill = "blue", stat = "identity")
p1
```

## Device test set

```{r Test}
dim(test)
names(test)
str(test)
summary(test)
head(test)

```
### Observation

### Visualization
Device_type
```{r Test device-type}
p2 <- test %>%
  group_by(device_type) %>%
  summarize(count=length(device_type)) %>%
  ggplot(aes(x =device_type, y = count)) +
    geom_bar(fill = "black", stat = "identity")

p2
```

```{r Test vs. Train Device_type}
install.packages('gridExtra', repos="http://cran.rstudio.com/")
library(gridExtra)
grid.arrange(p1, p2)
```

##Cookies

```{r Cookie}
dim(cookie)
names(cookie)
str(cookie)
summary(cookie)
head(cookie)
```
### Observation
There are 1555795 drawbridge_handle id.



## Ip

```{r Id all ip}
dim(ip)
names(ip)
str(ip)
summary(ip)
head(ip)
                   
```
### Observation

## Property


```{r Id all property}
dim(property)
names(property)
str(property)
summary(property)
head(property)
```
### Observation

## Property Category

```{r Property category}
dim(property_category )
names(property_category )
str(property_category )
summary(property_category )
head(property_category )

```

### Observation

